---
title: 'Supplementary material for "Diaconis-Ylvisaker prior penalized likelihood for $p/n \to \kappa \in (0,1)$ logistic regression"'

author:
  - name: "Philipp Sterzinger"
    email: p.sterzinger@lse.ac.uk
    affiliation: London School of Economics
    url: https://www.lse.ac.uk/statistics/people/philipp-sterzinger
  - name: "Ioannis Kosmidis"
    email: ioannis.kosmidis@warwick.ac.uk
    affiliation: University of Warwick
    url: https://www.ikosmidis.com
date: last-modified
date-format: long
format: md
---

# Directory structure

```{r}
#| echo: false
#| message: false
library("tinytable")
library("JuliaCall")
R_pkgs <- data.frame(Package = sort(c("dplyr", "ggplot2", "colorspace", "ggpp", "patchwork", "tidyr", "lmtest", "detectseparation", "glmnet")))
for (pkg in R_pkgs$Package)
    library(pkg, character.only = TRUE)
s_info <- sessionInfo()
R_v <- s_info$R.version$version.string
R_pkgs_v <- R_pkgs |> transform(Version = sapply(R_pkgs$Package, function(pkg)
                                    s_info$otherPkgs[[pkg]]$Version))
rownames(R_pkgs_v) <- NULL
```

```{r}
#| echo: false
#| message: false
julia_pkgs <- data.frame(Package = sort(c("ColorSchemes", "Cuba", "DataFrames", "Distributions",
                                          "FastGaussQuadrature", "FiniteDiff", "InvertedIndices", "JLD2",
                                          "LaTeXStrings", "LineSearches", "NLsolve", "NonlinearSolve",
                                          "Optim", "Plots", "PrettyTables", "PrettyTables", "ProgressMeter",
                                          "RCall", "Roots", "SciMLBase", "StatsBase")))
julia_v <- JuliaCall::julia_eval("string(VERSION)")
julia_pkgs_v <- julia_pkgs |> transform(Version = sapply(julia_pkgs$Package, julia_installed_package))
rownames(julia_pkgs_v) <- NULL
```


The directory `code/` contains the R and Julia scripts that reproduce
all the numerical results and figures in the manuscript

> Sterzinger P, Kosmidis I (2024). Diaconis-Ylvisaker prior penalized likelihood for $p/n \to \kappa \in (0,1)$ logistic regression. https://arxiv.org/abs/2311.07419

and the Supplementary Material document [`mDYPL-supplementary.pdf`](mDYPL-supplementary.pdf).

The directory `code/methods/` contains methods that the scripts in `code/` use.

The directory `results/` is populated by files that store the
numerical results the scripts produce. 

The directory `figures/` is populated by graphics that the scripts
produce.

# R version and contributed packages

All results are reproducible using `{r} R_v` and the contributed
packages
```{r}
#| echo: false
tt(R_pkgs_v)
```
and Julia version `{r} julia_v` and the contributed packages
```{r}
#| echo: false
tt(julia_pkgs_v)
```

# Reproducing the results


## Path

All scripts specify the path to the supplementary material path as
`supp_path`. This is currently set to `.` assuming that the working
directory for Julia and R is set to the current `git` repository. If
this is not the case for your setup, you should set `supp_path`
appropriately.

## Parallel computation

In each of the R and Julia scripts relying on parallel computation,
`n_cores` (currently set to `10`) sets the number of cores to use.

Computation on the R scripts that require it relies on parallel
computing, which is implemented through the `parallel` R package. The
script will not work on Windows unless `n_cores <- 1` (which will lead
in long compute times and is not recommended) or it is modified to use
a different parallel back-end. All results should be reproducible in
Unix-based systems (e.g. macOS and Linux). 

Parallel computing in the Julia scripts uses the Julia packages
`Distributed` and `Threads`. See [Parallel
Computing](https://docs.julialang.org/en/v1/manual/parallel-computing/)
in Julia's documentation for more details, and for setting the number
of threads.

## Details

The following table lists the R and Julia scripts that need to be
executed in order to reproduce the results. The table also lists the
outputs from each script, and their label if they are shown in the
main text or the Supplementary Material document. Some of the outputs
are intermediate results, so the scripts should be executed in the
order shown.


| Script                                                                                        | Output                                                                                 | Label     |
|-----------------------------------------------------------------------------------------------|----------------------------------------------------------------------------------------|-----------|
| [01-1-rescaled-mDYPL-estimators-1.jl](code/01-1-rescaled-mDYPL-estimators-1.jl)               | [rescaled-mDYPL-estimates-figure-1.rda](results/rescaled-mDYPL-estimates-figure-1.rda) |           |
| [01-1-rescaled-mDYPL-estimators-2.jl](code/01-1-rescaled-mDYPL-estimators-2.jl)               | [rescaled-mDYPL-estimates-figure-2.rda](results/rescaled-mDYPL-estimates-figure-2.rda) |           |
| [01-2-rescaled-mDYPL-estimators-outputs-1.R](code/01-2-rescaled-mDYPL-estimators-outputs-1.R) | [mdypl-vs-truth-1.pdf](figures/mdypl-vs-truth-1.pdf)                                   | Figure 1  |
| [01-2-rescaled-mDYPL-estimators-outputs-2.R](code/01-2-rescaled-mDYPL-estimators-outputs-2.R) | [mdypl-vs-truth-2.pdf](figures/mdypl-vs-truth-2.pdf)                                   | Figure S1 |
| [02-1-rescaled-PLR-statistics.jl](code/02-1-rescaled-PLR-statistics.jl)                       | [qqplots-rescaled-plr.rda](results/qqplots-rescaled-plr.rda)                           |           |
| [02-2-rescaled-PLR-statistics-outputs.R](code/02-2-rescaled-PLR-statistics-outputs.R)         | [qqplots-rescaled-plr.pdf](figures/qqplots-rescaled-plr.pdf)                           | Figure 2  |
| [03-1-abias-amse.jl](code/03-1-abias-amse.jl)                                                 | [abias-amse.rda](results/abias-amse.rda)                                               |           |
| [03-2-abias-amse-outputs.R](code/03-2-abias-amse-outputs.R)                                   | [abias-amse.pdf](figures/abias-amse.pdf)                                               | Figure 3  |
| [04-adaptive-shrinkage-table.jl](code/04-adaptive-shrinkage-table.jl)                         |                                                                                        | Table 1   |
| [05-1-min-mse.jl](code/05-1-min-mse.jl)                                                       | [alpha-min-mse.rda](results/alpha-min-mse.rda)                                         |           |
| [05-2-mu=1.jl](code/05-2-mu=1.jl)                                                             | [mu=1.rda](results/mu=1.rda)                                                           |           |
| [05-3-mu=1-outputs.R](code/05-3-mu=1-outputs.R)                                               | [alpha-unbiased-min-mse.pdf](figures/alpha-unbiased-min-mse.pdf)                       | Figure 4  |
| [06-1-cLS-comparison.jl](code/06-1-cLS-comparison.jl)                                         | [cLS-MDYPL-comparison-*.rda](results/)                                                 |           |
| [06-2-cLS-comparison-outputs.R](code/06-2-cLS-comparison-outputs.R)                           | [cLS-vs-mDYPL-estimation-inference.pdf](figures/cLS-vs-mDYPL-estimation-inference.pdf) | Figure 5  |
| [07-1-min-mse-ml-mdypl-ridge.jl](code/07-1-min-mse-ml-mdypl-ridge.jl)                         | [state_evolution_mDYPL.rda](results/state_evolution_mDYPL.rda)                         |           |
|                                                                                               | [state_evolution_ridge.rda](results/state_evolution_ridge.rda)                         |           |
|                                                                                               | [state_evolution_ML.rda](results/state_evolution_ML.rda)                               |           |
| [07-2-min-mse-ml-mdypl-ridge-outputs.R](code/07-2-min-mse-ml-mdypl-ridge-outputs.R)           | [rlr_mse_scaled_plots.pdf](figures/rlr_mse_scaled_plots.pdf)                           | Figure 6  |
| [08-1-intercept-simul-quantile-tables.jl](code/08-1-intercept-simul-quantile-tables.jl)       | [intercept_simul-plr-stat-quants.csv](results/intercept_simul-plr-stat-quants.csv)     |           |
|                                                                                               | [intercept-simul-z-stat-quants.csv](results/intercept-simul-z-stat-quants.csv)         |           |
|                                                                                               |                                                                                        | Table 2   |
|                                                                                               |                                                                                        | Table S1  |
|                                                                                               |                                                                                        | Table S2  |
| [09-1-mfeat-case-study.R](code/09-1-mfeat-case-study.R)                                       | [case-study-probs.pdf](figures/case-study-probs.pdf)                                   | Figure 7  |
| [09-2-mfeat-simulation.R](code/09-2-mfeat-simulation.R)                                       | [fou+kar-simu*.rda](results/)                                                          |           |
| [09-3-mfeat-simulation-outputs.R](code/09-3-mfeat-simulation-outputs.R)                       | [case-study-qqplots.pdf](figures/case-study-qqplots.pdf)                               | Figure 7  |
| [10-beta-norm-simul.jl](code/10-beta-norm-simul.jl)                                           | [beta_l2_length*.jld2](results/)                                                       |           |
|                                                                                               | [beta_norm_alphas.pdf](figures/beta_norm_alphas.pdf)                                   | Figure S2 |
|                                                                                               | [beta_norm.pdf](figures/beta_norm.pdf)                                                 | Figure S2 |
| [11-1-eta-bounds.jl](code/11-1-eta-bounds.jl)                                                 | [upsilon-gamma.rda](results/upsilon-gamma.rda)                                         |           |
| [11-2-eta-gamma-outputs.R](code/11-2-eta-gamma-outputs.R)                                     | [cLS-MDYPL-upsilon.pdf](figures/cLS-MDYPL-upsilon.pdf)                                 | Figure S3 |
|                                                                                               | [upsilon-gamma.pdf](figures/upsilon-gamma.pdf)                                         | Figure 8  |



